Excuse me, do you have a moment to talk about version control?

### 2017-05-18 README.Rmd
First success using the rticles templagte :tada:

---
title: "Excuse me, do you have a moment to talk about version control?"
author: "Jenny Bryan"
date: "`r format(Sys.Date())`"
output:
  github_document:
    toc: true
---

@@

There many benefits of using hosted version control in your statistical practice:

@@

*here's one way I see phylogeny in my mind*
![](https://upload.wikimedia.org/wikipedia/commons/2/2b/Phylogeny_of_Retroviruses.jpg)

*make such a phylogeny with a set of crazy filenames like this*
![](https://www.onshape.com/hs-fs/hub/379003/file-2533844795-jpg/Blog_Assets/Version_Control_Graphic-2.jpg?t=1494963046029)

*or riff on the famous PhD Comic*
![](http://phdcomics.com/comics/archive/phd101212s.gif)

>>>>

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- affiliation: RStudio and the Department of Statistics, University of British Columbia
  name: Jennifer Bryan
  thanks: The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton and Colin Rundel.
blinded: 0
output:
  rticles::asa_article:
    pandoc_args: --listings
  github_document:
    toc: yes
keywords: version control
abstract: Abstract abstract abstract.
---

```{r}
is_github_document <-
  knitr::opts_knit$get("rmarkdown.pandoc.to") == "markdown_github"
```

@@

There are many benefits of using hosted version control in your statistical practice:

@@

*If you're looking at the PDF draft, you're missing out on some figures around here in the GitHub Markdown version that hint at the figure I plan to embed.*

```{r eval = is_github_document, echo = FALSE, results = 'asis'}
cat("*here's one way I see phylogeny in my mind*\n")
cat("![](https://upload.wikimedia.org/wikipedia/commons/2/2b/Phylogeny_of_Retroviruses.jpg)")

cat("*make such a phylogeny with a set of crazy filenames like this*\n")
cat("![](https://www.onshape.com/hs-fs/hub/379003/file-2533844795-jpg/Blog_Assets/Version_Control_Graphic-2.jpg?t=1494963046029)")

cat("*or riff on the famous PhD Comic*")
cat("![](http://phdcomics.com/comics/archive/phd101212s.gif)")
```
